---
title: "Wyklad04"
author: "Lucjan Janowski"
date: "7 grudnia 2016"
output: html_document
runtime: shiny
---

Na podstawie Edwin de Jonge, Mark van der Loo, "An introduciton to data cleaning with R" rok 2013 oraz strony Pogromcy danych.

Przyklad pierwszy.

```{r}
install.packages("PogromcyDanych")
library(PogromcyDanych)
summary(auta2012)
hist(auta2012$Przebieg.w.km)

nrow(auta2012)

summary(auta2012$Przebieg.w.km)

przebieg = auta2012$Przebieg.w.km[!is.na(auta2012$Przebieg.w.km)]

hist(log(przebieg))

fplot(przebieg[przebieg>exp(13) & przebieg<4*10^8])
exp(13)

max(przebieg)
((max(przebieg)/100)/24)/365

((exp(13)/100)/24)/365

#600000 - na rok, ale takie auta żyją 5-6 lat
#Ta informacja wymaga interakcji z zewnetrznym swiatem ;)
```


```{r}
bity = c(2.3, 4.5, 1.2, 2.1, 0.8, 1.2, 1.4, 1.5, 2.8, 2.5, 3.5, 4.5, 21, 1.2, 3.4, 1.4, 2.4, 2.3, 1.4)
summary(bity)
plot(bity)
```



Specjalne dane, NA, NULL, Inf oraz NaN

```{r}
NA+1
sum(c(NA, 3, 5, 6))
sum(c(NA, 3, 5, 6), na.rm=TRUE)
length(c(NA, 2, 3, 4))
3 == NA
TRUE | NA

NULL+1
sum(c(NULL, 3, 5, 6))
length(c(NULL, 2, 3, 4))
3 == NULL
TRUE | NULL

Inf+1
sum(c(Inf, 3, 5, 6))
length(c(Inf, 2, 3, 4))
3 == Inf
Inf == Inf
TRUE | Inf

0/0
Inf-Inf
NaN+1
sum(c(NaN, 3, 5, 6))
length(c(NaN, 2, 3, 4))
3 == NaN
FALSE | NaN
TRUE | NaN
```

Prpszę wczutać plik pomiaryZapylenia.txt oraz doprowadzić do otrzymania poprawnego technicznie zbioru danych.

Implementacja przepisana z: Edwin de Jonge, Mark van der Loo, "An introduciton to data cleaning with R" rok 2013. 

```{r}
hboutlier <- function(x, r){
  x <- x[is.finite(x)]
  stopifnot(
    length(x) > 0
    , all(x>0)
  )
  xref <- median(x)
  if (xref <= sqrt(.Machine$double.eps))
    warning("Reference value close to zero: results may be inaccurate")
  pmax(x/xref, xref/x) > r
}

x <- rgamma(1000, 2, 0.01)
x <- append(x, c(0.4))
min(x)
plot(x)
hist(x)
hist(x,100)
x[hboutlier(x,100)]
x[hboutlier(x,10)]
sum(x[hboutlier(x,5)]>median(x))

boxplot.stats(x)$out
boxplot.stats(x, coef = 3)$out
```


Przykład kodu wcczytującego dane z eksperymentu i doprowadzającego do poprawnie technicznych danych.

```{r}
AGH = read.csv("AGHOriginalData_withComma.csv", sep = ",", header=TRUE, colClasses = c("factor", "numeric", "character", "factor", "character", "character", "factor", "character", "character", "numeric", "numeric", "character", "character"))

#removing not needed columns
AGH$Camera = NULL
AGH$Comments = NULL
AGH$X = NULL
AGH$LabID = rep("AGH", nrow(AGH))
#converting data, especially the time data
Sys.setlocale("LC_TIME", "pl_PL.UTF-8")
AGH$SessionStartTime <- as.POSIXct(strptime(AGH$SessionStartTime, "%d %h %Y %H:%M:%S"))

#creating one variable
rawData = rbind(AGH)

list = ls()
rm(list = list[list != "rawData"])

#converting data, especially the time data
Sys.setlocale("LC_TIME", "en_GB.UTF-8")

rawData$TaskStartTime <- as.POSIXct(strptime(rawData$TaskStartTime, "%H:%M:%S"))
rawData$TaskEndTime <- as.POSIXct(strptime(rawData$TaskEndTime, "%H:%M:%S"))
rawData$LabID <- as.factor(rawData$LabID)
rawData$UserID[rawData$LabID == "AGH"] <- 1000 + rawData$UserID[rawData$LabID == "AGH"]
rawData$UserID <- as.factor(rawData$UserID)

#separate mos and pair experiments
pairRaw = rawData[rawData$StudyType == "Comparison Study", ]

#Only Pair is analyzed untill it is saved, than mosRaw is analyzed

#Correcting some factors
pairRaw$ScreenSelected <- factor(pairRaw$ScreenSelected, levels = c("Left", "Right"))

#Extracting file name
pairRaw$ImageName = gsub(".jpg", "", pairRaw$ImageName)
pairRaw$ImageName = gsub(".JPG", "", pairRaw$ImageName)
pairRaw$ImageName = gsub("..\\s", "", pairRaw$ImageName)
pairRaw$ImageName = gsub("Parking_dev", "", pairRaw$ImageName)
#at this point ImageName is wrong since the folger is left

#extracting information about the folder and the pair
tmp = strsplit(pairRaw$FolderPath, "\\", fixed = TRUE)
tmp2 = matrix(unlist(tmp), ncol=5, byrow = TRUE)
tmpPhoto = as.factor(tmp2[,4])
#unique names for Photo variable
levels(tmpPhoto)[levels(tmpPhoto) == "AutumnMtn"] <- "Autumn"
levels(tmpPhoto)[levels(tmpPhoto) == "Beach Toys"] <- "Beach"
levels(tmpPhoto)[levels(tmpPhoto) == "Building Corner"] <- "Corner"
levels(tmpPhoto)[levels(tmpPhoto) == "Evacuation Plan"] <- "Evac"
levels(tmpPhoto)[levels(tmpPhoto) == "Green Tree"] <- "Green"
levels(tmpPhoto)[levels(tmpPhoto) == "Mirror Ball"] <- "Mirror"
levels(tmpPhoto)[levels(tmpPhoto) == "Tree Lake"] <- "Tree"
pairRaw$PhotoClass <- tmpPhoto

tmpPair = strsplit(tmp2[,5], " ", fixed = TRUE)
tmpPair2 = matrix(unlist(tmpPair), ncol=2, byrow = TRUE)
photo1 = as.factor(tmpPair2[,1])
photo2 = as.factor(tmpPair2[,2])
pairRaw$Image1 = interaction(pairRaw$PhotoClass, photo1)
pairRaw$Image2 = interaction(pairRaw$PhotoClass, photo2)
pairRaw$ImageSelected = interaction(pairRaw$PhotoClass, as.factor(pairRaw$ImageName))

#to uniform the forctors, the pool of images 
pairRaw$Image1 <- factor(pairRaw$Image1, levels = unique(c(levels(pairRaw$Image1), levels(pairRaw$Image2), levels(pairRaw$ImageSelected))))
pairRaw$Image2 <- factor(pairRaw$Image2, levels = unique(c(levels(pairRaw$Image1), levels(pairRaw$Image2), levels(pairRaw$ImageSelected))))
pairRaw$ImageSelected <- factor(pairRaw$ImageSelected, unique(c(levels(pairRaw$Image1), levels(pairRaw$Image2), levels(pairRaw$ImageSelected))))

#correcting AGH data
ind1 = pairRaw$LabID == "AGH" & pairRaw$ImageSelected == pairRaw$Image1
ind2 = pairRaw$LabID == "AGH" & pairRaw$ImageSelected == pairRaw$Image2
pairRaw$ImageSelected[ind1] = pairRaw$Image2[ind1]
pairRaw$ImageSelected[ind2] = pairRaw$Image1[ind2]
#ind1 = pairRaw$LabID == "AGH" & pairRaw$ScreenSelected == "Left"
#ind2 = pairRaw$LabID == "AGH" & pairRaw$ScreenSelected == "Right"
#pairRaw$ImageSelected[ind1] = "Right"
#pairRaw$ImageSelected[ind2] = "Left"

#Image name per side
pairRaw$LeftImage = pairRaw$Image1
pairRaw$RightImage = pairRaw$Image2

ind = pairRaw$ScreenSelected == "Left" & pairRaw$Image1 == pairRaw$ImageSelected
pairRaw$LeftImage[ind] = pairRaw$Image1[ind]
pairRaw$RightImage[ind] = pairRaw$Image2[ind]
ind = pairRaw$ScreenSelected == "Left" & pairRaw$Image2 == pairRaw$ImageSelected
pairRaw$LeftImage[ind] = pairRaw$Image2[ind]
pairRaw$RightImage[ind] = pairRaw$Image1[ind]
ind = pairRaw$ScreenSelected == "Right" & pairRaw$Image1 == pairRaw$ImageSelected
pairRaw$LeftImage[ind] = pairRaw$Image2[ind]
pairRaw$RightImage[ind] = pairRaw$Image1[ind]
ind = pairRaw$ScreenSelected == "Right" & pairRaw$Image2 == pairRaw$ImageSelected
pairRaw$LeftImage[ind] = pairRaw$Image1[ind]
pairRaw$RightImage[ind] = pairRaw$Image2[ind]
```

